Limited information strategies for topological games

### 2015-03-13 phd/talks-and-presentations/2015-03-11-defense.tex
add in pauses to slides
remove redundant question

\begin{document}
\renewcommand{\pause}{}
\newcommand{\vspacing}{\vspace{1em}}
\newcommand{\vpause}{\pause\vspacing}

@@

  The aim of my dissertation was to investigate four topological games
  from the literature with unknown limited information implications.

@@

  Note that for each $F\in[\omega_1]^{<\omega}$, there is some $n_F<\omega$
  such that $f_{\alpha+1}(\beta)<n_F$ for all $\beta,\alpha\in F$.

>>>>

\begin{document}
% \renewcommand{\pause}{}
\newcommand{\vspacing}{\vspace{1em}}
\newcommand{\vpause}{\pause\vspacing}

@@

  In my dissertation I investigate four topological games
  from the literature to find new limited information characterizations.

@@

  Note that for each $F\in[\omega_1]^{<\omega}$, there is some $n_F<\omega$
  such that $f_{\alpha+1}(\beta)<n_F$ for all $\beta\leq\alpha\in F$.
